Automatic Matching of Bullet Lands

### 2017-06-22 imaging-paper.Rnw
line break in facet

ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), ymin=-6, ymax=6, data=res$lines, alpha=0.2, show.legend=FALSE) +
  geom_line(aes(x = y, y = l30, linetype = bullet),  data = res$bullets) +
  scale_linetype_discrete("") + ylab("") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1), legend.justification=c(1,1)) + 
  ylim(c(-6,7)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match)) +
    ylab(expression(paste("Signatures (in ",mu,"m)", sep=""))) +
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  theme(text = element_text(size=15))
@
\caption{\label{fig:mismatch}Known mismatch with a relatively large number of maximal consecutive matching striae (twelve) in the middle. The pattern in the middle does look surprisingly similar, however the outer ends of the signatures easily reveals this comparison as mismatch. }
\end{figure}

@@

dm <- melt(densities, measure.var=c("KM", "KNM"))
dm$var <- factor(dm$var, levels=features)
levels(dm$var)[3:4] <- c("#matches", "#non-matches")
levels(dm$variable) <- c("Known matches\n(KM)", "Known non-matches\n(KNM)")
dm$varLabel <- dm$var
levels(dm$varLabel) <- c(
  "Consecutive Matching\n Striae (CMS)", 
  "Consecutive Non-Matching\n Striae (CNMS)",
  "#matches",
  "#non-matches",
  "Average difference (D)",
  "Sum of peaks (S)",
  "Cross-correlation\n function (ccf)")

>>>>

ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), ymin=-6, ymax=6, data=res$lines, alpha=0.2, show.legend=FALSE) +
  geom_line(aes(x = y, y = l30, linetype = bullet),  data = res$bullets) +
  scale_linetype_discrete("") + ylab("") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1), legend.justification=c(1,1)) + 
  ylim(c(-6,7)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match)) +
    ylab(expression(paste("Signatures (in ",mu,"m)", sep=""))) +
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  theme(text = element_text(size=15), legend.background = element_rect(fill="transparent"))
@
\caption{\label{fig:mismatch}Known mismatch with a relatively large number of maximal consecutive matching striae (twelve) in the middle. The pattern in the middle does look surprisingly similar, however the outer ends of the signatures easily reveals this comparison as mismatch. }
\end{figure}

@@

dm <- melt(densities, measure.var=c("KM", "KNM"))
dm$var <- factor(dm$var, levels=features)
levels(dm$var)[3:4] <- c("#matches", "#non-matches")
levels(dm$variable) <- c("Known matches\n(KM)", "Known non-matches\n(KNM)")
dm$varLabel <- dm$var
levels(dm$varLabel) <- c(
  "Consecutive Matching\n Striae (CMS)", 
  "Consecutive Non-Match-\ning Striae (CNMS)",
  "#matches",
  "#non-matches",
  "Average difference (D)",
  "Sum of peaks (S)",
  "Cross-correlation\n function (ccf)")
